Finding Functional Bugs in JavaScript Engines with Differential Testing---an Experience Report

### 2018-06-10 paper/paper.tex
pass on methodology

Figure~\ref{fig:workflow} illustrates the workflow of the
infrastructure we used in this study. Boxes denote encapsulation,
arrowed lines indicate control flow (dashed) and data flow (filled),
and the cyclic icons denote repetition. In this case, it indicates
that each test file will be proceseed in separate and, if fuzzing is
selected, a single file can be processed multiple times--one for each
of its fuzzed variants. The bug-finding process takes on input JS
files from regression test suites of various JS
engines. Table~\ref{tab:test-suites} shows the JS sources we mined
from online repositories of various open-source engines. Overall, we
found a total of \Fix{XX} JS files.

@@

The bug-finding process works as follows.  Considering the case
fuzzing is not selected, as illustrated in the inner box at the bottom
of the figure, the oracle checks whether or not the output
produced for that file is consistent across all engine
implementations. In case the test passes in all engines or fails in
all engines (\ie{}, the output is consistent), the infrastructure
discards the corresponding input. Otherwise, it considers the input as
potentially fault-revealing; hence interesting for human
inspection. Considering the case where fuzzing~\cite{fuzz-testing-history}
is selected, new inputs are obtained from a given input using some
off-the-shelf fuzzer\footnote{Several fuzzing methods have been proposed in
the past, varying with respect to how new inputs are generated (\eg{},
coverage-based~\cite{afl,honggfuzz},
grammar-based~\cite{grammarinator,jsfunfuzz}, and
random-based~\cite{radamsa}).}. The workflow is similar to that of no
fuzzing. In this case, however, multiple warnings can be produced for
a given seed input.

@@

\subsection{Constants.}~We used the following engines in
this study: Microsoft's Chakra~\Fix{cite}, Google's v8~\Fix{cite},
Mozilla's SpiderMonkey~\Fix{cite}, and Apple's JavaScriptCore
(WebKit)~\Fix{cite}. We selected these engines based on
popularity. Note that they represent the main players in web
technology. \Fix{versions}

@@

Our dependent/effect variable is bug-finding ability. We consider a
search successful only if it lends in a bug confirmed by developers or
the affected engine. For the independent experimental variables, we
considered: seeds, fuzzing strategy, and combination of fuzzers. In
short, our experiment assesses the impact of these factors in
bug-finding ability.

Considering the seed factor, we want to observe how often fuzzing
really helps. In the limit, all bugs could be found without extra
inputs, \ie{}, executing the seed input on each engine and comparing
their outcomes. Considering the fuzzing strategy, it is important to
understand whether a particular strategy or implementation is
prominent. Finally, \Fix{not sure if we should consider this
  dimension...}

>>>>

Figure~\ref{fig:workflow} illustrates the workflow of the
infrastructure we used in this study. Boxes denote encapsulation;
arrowed lines indicate control flow (dashed) and data flow
(filled). The cyclic icons denote repetition--the leftmost cyclic icon
indicates that each file in the input list will be analyzed in
separate and the rightmost icon indicates that a single file will be
processed multiple times in fuzzing mode. The bug-finding process
takes on input JS files from regression test suites of various JS
engines. Table~\ref{tab:test-suites} shows the JS sources we mined
from online repositories of various open-source engines. Overall, we
found a total of \Fix{XX} JS files.

@@

The bug-finding process works as follows.  Considering the case
fuzzing is not selected, as illustrated in the inner box at the bottom
of the figure, the oracle checks whether or not the output produced
for that file is consistent across all engine implementations. In case
the test passes in all engines or fails in all engines (\ie{}, the
output is consistent), the infrastructure discards the corresponding
input (mark ....). Otherwise, it considers the input as potentially
fault-revealing; hence interesting for human inspection. Considering
the case where fuzzing~\cite{fuzz-testing-history} is selected, new
inputs are obtained from a given input using some off-the-shelf
fuzzer\footnote{Several fuzzing methods have been proposed in the
  past, varying with respect to how new inputs are generated (\eg{},
  coverage-based~\cite{afl,honggfuzz},
  grammar-based~\cite{grammarinator,jsfunfuzz}, and
  random-based~\cite{radamsa}).}. The workflow is similar to that of
no fuzzing. In this case, however, multiple warnings can be produced
for a given seed input.

@@

\subsection{Constants.}~We used the following engines in
this study: Microsoft's Chakra~\Fix{cite}, Google's v8~\Fix{cite},
Mozilla's SpiderMonkey~\Fix{cite}, and Apple's JavaScriptCore
(WebKit)~\Fix{cite}. We selected these engines based on
popularity~\Fix{cite}. Considering fuzzing tools, we used
representatives of the most popular approaches to fuzzing. For
random-based fuzzing, we used Radamsa~\cite{radamsa}; for
coverage-based fuzzing, we used
\Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
generative-based fuzzing, we used
\Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
be found elsewhere~\cite{fuzz-bart}.

@@

The independent variable of our experiment is the fuzzing strategy as
represented by various fuzzing tools. Our dependent variables are (i)
the ratio of bugs found with fuzzing as opposed to no fuzzing and (ii)
and the ratio of bugs found for each fuzzing strategy. We consider a
search successful only if it lends in a bug confirmed by the
developers of the affected engine. In short, our experiment assesses
the impact of these factors in bug-finding ability.

Considering the ratio of bugs found with fuzzing versus no fuzzing, we
want to observe how often fuzzing really helps. In the limit, all bugs
could be found without extra inputs, \ie{}, simply executing the seed
inputs on each engine and comparing their outcomes. Recall that we
mined test suites from a variety of sources. Considering the fuzzing
strategy, it is important to understand whether a fuzzing strategy is
particularly prominent.
